Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-10-26 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
References added #50
I hope I modified the correct file.

As a volunteer based system, there are some issues worth 
noting:\begin{enumerate}
\item Volunteers are anonymous, only the IP address sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer  misbehaves in some way the provider cannot 
prosecute or discipline the volunteer.
\item Participants must also trust the application provider, 
regarding invation of privacy, the integrity of their devices 
and intended application. 
\end{enumerate}

>>>>

As a volunteer based system, there are some issues worth 
noting \cite{sarmenta2001volunteer,web:BOINC} :\begin{enumerate}
\item Volunteers are anonymous, only the IP address sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer  misbehaves in some way the provider cannot 
prosecute or discipline the volunteer.
\item Participants must also trust the application provider, 
regarding invation of privacy, the integrity of their devices 
and intended application. 
\end{enumerate}
In this work security aspects related to sabotage and 
trust management (e.g. \cite{domingues2007sabotage}) have not been addressed.
